---
title: "MP2 Technical Report: "
author: "Katy Cummings, Tulip Daaboul, Michel Ruiz-Fuentes"
format: pdf
editor: visual
date: "`r Sys.Date()`"
indent: true
---

## Introduction

## Methodology

## Results

[**Load Data:**]{.underline}

```{r, LOADPKGE, warning=F, message=F, echo=FALSE}
library(tidyverse)
library(rio)
library(asbio)
library(dplyr)
library(ggplot2)

milk_df1 <- import("milk_cleaned_data.csv")
```

[**Descriptive Statistics**]{.underline}:

```{r, SUMMARYSTATS, warning=F, message=F, echo=FALSE}
#TREATMENT GROUP STATS
milk_summary <- 
  milk_df1 |>
  group_by(treatment) |>
  summarise(group_mean=mean(consumer_likelihood), 
            group_n=n(), 
            group_sd=sd(consumer_likelihood),
            group_min= min(consumer_likelihood),
            group_max= max(consumer_likelihood))  
milk_summary
```

[**Condition Check 1 Variability & Standard Deviation**]{.underline}:

Our largest standard deviation \[`Plant Control & Dairy Control`\] 1.38 divided by the smallest standard deviation \[`DairyCon(-)`\] 1.05 equals 1.31. Their quotient is smaller than 2, so we do not violate the condition about constant variance for our ANOVA model.

```{r, CONDI01, warning=F, message=F, echo=FALSE}
#STANDARD DEVIATION (constant variance)
1.38/1.05
```

[**Condition Check 2 Constant Variance**]{.underline}:

In our density plot, we view the distribution of the `Consumer Likelihood` at the different levels of the `Milk (ad type and sentiment)` treatment. The data is not normally distributed nor unimodal among all levels. While the data distributions for the `Plant_control` and `PlantPro(+)` are normal, the other distributions vary. For example, `DairyCon` and `Plant_control` is bimodal, `Dairy control` and `DairyPro` is right-skewed. Therefore, we have violated the condition about constant variance for our ANOVA model.

```{r, CONDI02, warning=F, message=F, echo=FALSE}
#DENSITY PLOT (normal distribution)
milk_distribution <-
  ggplot(data=milk_df1, aes(x=consumer_likelihood, color=treatment)) + 
  geom_density() + 
  labs(title ="Consumer Likelihood Density Plot",
      subtitle= "Assessing Distribution by Milk Treatment",
      caption ="source: Qualtrics Milk Data") +
  xlab("Treatment") +
  ylab ("Consumer Likelihood") 
milk_distribution
```

[**Condition Check 3 Symmetrical Distribution around Group Means**]{.underline}:

```{r, CONDI03, warning=F, message=F, echo=FALSE}
#BOX PLOT (constant variance)
milk_means <-
  ggplot(data=milk_df1, aes(x=consumer_likelihood, y=treatment)) + 
  geom_boxplot(fill="darkseagreen3") + 
  stat_summary(fun="mean") + 
  labs(title ="Consumer Likelihood Box Plot",
      subtitle= "Assessing Distribution by Treatment",
      caption ="source: Qualtrics Milk Data") +
  xlab("Treatment") +
  ylab ("Consumer Likelihood") 
milk_means
```

[**Conditions Interpretation & Transformation:**]{.underline}

[**Two-Way ANOVA Model**]{.underline}:

```{r, MOD01, warning=F, message=F, echo=FALSE}
```

[**Interaction Model**]{.underline}:

```{r, MOD02, warning=F, message=F, echo=FALSE}
```

[**Independent residuals:**]{.underline}

```{r, RESIDCHECK01, warning=F, message=F, echo=FALSE}
```

[**Normally Distributed Residuals**:]{.underline}

```{r, RESIDCHECK02, warning=F, message=F, echo=FALSE}
```

[**Confidence Intervals & Effect Size**]{.underline}:

```{r, CI, warning=F, message=F, echo=FALSE}
```

[**R-Squared:**]{.underline}

```{r, RSQUARED, warning=F, message=F, echo=FALSE}
```

## Conclusion
